---
title: "Analysing scraped data on Facebook Marketplace listings"
output: html_notebook
---

# Analysing scraped data on Facebook Marketplace listings

We've scraped data using OutWit Hub. Now we import it in:

```{r}
scrapeddata <- read.csv("marketplacescrape.csv", stringsAsFactors = F)
```

This is what it looks like:

```{r}
head(scrapeddata)
```

Let's delete that first column:

```{r}
scrapeddata <- scrapeddata[c(-1)]
head(scrapeddata)
```

And let's split the location column, which has 2 different pieces of data:

```{r}
head(scrapeddata$Location)
```

We [need the `separate()` function](https://tidyr.tidyverse.org/reference/separate.html) from the Tidyverse for the next bit:

```{r}
library(tidyverse)
#Separate the Location column into 2 new columns, don't remove the original column
scrapeddata <- separate(scrapeddata, Location, into = c("loconly","timestamp"), sep = " · ", remove = F,
  convert = FALSE, extra = "warn", fill = "warn")
```

And let's show a table of results:

```{r}
#Create a dataframe from a table of results
places <- data.frame(table(scrapeddata$loconly))
#attach it to sort
attach(places)
#sort by the Freq column
places <- places[order(-Freq),]
#detach
detach(places)
#Show the results
head(places, 20)
```

## Removing duplicates

We do have a lot of entries which appear in multiple searches, however, so let's try to remove those.

First we need to create a way of uniquely identifying each entry - this can simply be a combination of all the information:

```{r}
#Combine 4 cells to create a concatenated one
scrapeddata$alltext <- paste(scrapeddata$Price, scrapeddata$Title, scrapeddata$Location, scrapeddata$timestamp, sep=":")
```

Next we ask to remove duplicates using [the `duplicated()` function](https://www.datanovia.com/en/lessons/identify-and-remove-duplicate-data-in-r/):

```{r}
#adapted from https://stackoverflow.com/questions/24011246/deleting-rows-that-are-duplicated-in-one-column-based-on-the-conditions-of-anoth
scrapeddata.nodups = scrapeddata[!duplicated(scrapeddata$alltext),]
```

This leaves us with around 3,000 entries - removing more than 5,000 duplicates.

(A better approach would be to use the listing ID but the scraping didn't always capture this.)

Now repeat the places analysis:

```{r}
#Create a dataframe from a table of results
places <- data.frame(table(scrapeddata.nodups$loconly))
#attach it to sort
attach(places)
#sort by the Freq column
places <- places[order(-Freq),]
#detach
detach(places)
#Show the results
head(places, 20)
```

That looks much more like what we are seeing on the pages.

Let's export that too:

```{r}
write.csv(places, "topplaces.csv")
```



## Extracting the words

Next we analyse the text - this is done in a separate notebook.
