---
title: "Analysing scraped data on Facebook Marketplace listings"
output: html_notebook
---

# Counting text in scraped data on Facebook Marketplace listings

We've scraped data using OutWit Hub and imported it in a separate notebook. This notebook focuses on the text analysis.

## Extracting the words

These steps are adapted from a [previous notebook](https://github.com/BBC-Data-Unit/art-uk/blob/master/keyword_counting.Rmd):

```{r}
#The keywords are in the Title column
write.csv(scrapeddata.nodups$Title, 'keywordsastext.txt')
```

Now we re-import that data as a character object using `scan`:

```{r}
keywords <- scan('keywordsastext.txt', what="char", sep=",")
# We convert all text to lower case to prevent any case sensitive issues with counting
keywords <- tolower(keywords)
#Remove brackets, ampersands and numbers
keywords <- gsub("[()]","",keywords)
keywords <- gsub("[&]"," ",keywords)
keywords <- gsub("[£]","",keywords)
keywords <- gsub("[/]"," ",keywords)
keywords <- gsub("[-]"," ",keywords)
keywords <- gsub("[!]"," ",keywords)
keywords <- gsub("[,]"," ",keywords)
keywords <- gsub("[.]"," ",keywords)
keywords <- gsub("[']"," ",keywords)
keywords <- gsub("[0-9]","",keywords)
```

We now need to put this through a series of conversions before we can generate a table:

```{r}
keywords.split <- strsplit(keywords, " ")
keywordsvec <- unlist(keywords.split)
keywordstable <- table(keywordsvec)
```

That table is enough to create a CSV from:

```{r}
write.csv(keywordstable, 'keywordcount.csv')
```

## String distance for cleaning

Import that data as a data frame:

```{r}
keyworddata <- read.csv('keywordcount.csv', stringsAsFactors = F)
```

First, sort the data to bring the most common terms to the top:

```{r sort biggest to smallest}
attach(keyworddata)
keyworddata <- keyworddata[order(-Freq),]
detach(keyworddata)
head(keyworddata, 20)
```

Some rows we don't want: the first row is 'no keyword' (where elements have been replaced with nothing). Let's remove that:

```{r}
#Remove the first row
keyworddata <- keyworddata[-1,]
head(keyworddata, 20)
```


Let's also remove 'homemade', 'home made' and 'food' as these are all irrelevant to the analysis:

```{r}
keyworddata <- keyworddata[-1:-4,]
head(keyworddata, 30)
```

The "and", "for", and "with" could all be removed by index too...

...But this wouldn't be the same for each data frame. So let's replace them by matching them:

```{r}
#Find the index of the match
match("and", keyworddata$keywordsvec)
#Use that to remove that row
keyworddata <- keyworddata[-match("and", keyworddata$keywordsvec),]
#Check results
head(keyworddata, 20)
```

We need to repeat this for the others. There are so many, it could be more efficient to look for a list of 'stopwords' that we can loop through and exclude.

The [stopwords package](https://github.com/quanteda/stopwords) is one source of such a list.

```
if(!require(stopwords)){
  install.packages("stopwords")  
}
library(stopwords)

#We can print a list
stopwords::stopwords(language = "en",source = "snowball")

#Loop through that list
for(i in stopwords::stopwords(language = "en",source = "snowball")){
  #Match and remove it
  keyworddata <- keyworddata[-match(i, keyworddata$keywordsvec),]
}
#Check results
head(keyworddata, 40)
```

...But doing this removes all words, so a manual approach may be better given that we are only interested in the top 30 or so:

```{r remove stopwords}
keyworddata <- keyworddata[-match("for", keyworddata$keywordsvec),]
keyworddata <- keyworddata[-match("to", keyworddata$keywordsvec),]
keyworddata <- keyworddata[-match("of", keyworddata$keywordsvec),]
keyworddata <- keyworddata[-match("in", keyworddata$keywordsvec),]
keyworddata <- keyworddata[-match("or", keyworddata$keywordsvec),]
keyworddata <- keyworddata[-match("on", keyworddata$keywordsvec),]
keyworddata <- keyworddata[-match("a", keyworddata$keywordsvec),]
keyworddata <- keyworddata[-match("all", keyworddata$keywordsvec),]
keyworddata <- keyworddata[-match("the", keyworddata$keywordsvec),]
head(keyworddata, 40)
```

Let's export that again:

```{r}
write.csv(keyworddata, "keyworddata.csv")
```


## Variations in wording

We can see with the top 30 that 'samosa' and 'samosas' both appear - so we can use the top 20 as a basis to look for close matches elsewhere.

[The `stringdist` package](https://cran.r-project.org/web/packages/stringdist/stringdist.pdf) allows us to identify distances between strings (i.e. how many characters you would need to change) and the string with the closest distance:

```{r}
if(!require(stringr)){
  install.packages("stringdist")
  }
library(stringdist)
```

Try the `amatch` function:

```{r}
nearmatch <- stringdist::amatch(keyworddata$keywordsvec,keyworddata$keywordsvec,maxDist=3)
#We can't set a minDist - here's the help:
?amatch
```

We might try [a different approach](https://www.r-bloggers.com/natural-language-processing-in-r-edit-distance/) then:

Now we create a function to match:

```{r}
#Create the function
clean_name = function(raw_name, teamlist)
{
    #optional
    require(stringr)
    raw_name = str_trim(raw_name)
    
    #necessary
    ed_dist = adist(raw_name, teamlist)
    best = which(ed_dist == min(ed_dist))[1] # [1] breaks ties
    matchname <- teamlist[best]
    matchindex <- best
    return(c(matchname,matchindex)) # Return the best fitting name
}
```

And then use it:

```{r}
#Create an empty vector to store results
matchlist <- c()
matchcounts <- c()
#Run the function
for(i in keyworddata$keywordsvec[1:20]){
  print(i)
  #Find the nearest match
 nearestmatch_and_bestindex <- clean_name(i, keyworddata$keywordsvec[21:757])
 print(nearestmatch_and_bestindex)
 #Add it to the vector
 matchlist <- c(matchlist, nearestmatch_and_bestindex[1])
 #The vector coerces the number to a string because the other element is a string
 #So we need to convert it
 matchcounts <- as.numeric(c(matchcounts, nearestmatch_and_bestindex[2]))
}
```


```{r}
#Create new dataframe
top20 <- head(keyworddata, 20)
#Add to data frame
top20$nearmatch <- matchlist
#Create dataframe of the rest
matchdata <- keyworddata$Freq[21:757]
#Create an empty vector to store results
allcounts <- c()
#Loop through the indexes stored in the chunk above
for(i in matchcounts){
  #Print the index
  print(matchdata[i])
  #add to the vector by accessing the data at that index in matchdata
  allcounts <- c(allcounts, matchdata[i])
}
#Assign the new vector of 20 matches, as a new column
top20$matchcounts <- allcounts
#Show the whole data frame
top20
```

We can see that some matches are useful - chicken and chiken, for example - but most are not - e.g. house and horse.

We now have to manually combine the ones that we want.

We might also look at words that occur together alphabetically, e.g. curry and curries.

Let's do this for the top 40:

```{r}
#Create an empty vector to store results
matchlist <- c()
matchcounts <- c()
#Run the function
for(i in keyworddata$keywordsvec[1:40]){
  print(i)
  #Find the nearest match
 nearestmatch_and_bestindex <- clean_name(i, keyworddata$keywordsvec[41:757])
 print(nearestmatch_and_bestindex)
 #Add it to the vector
 matchlist <- c(matchlist, nearestmatch_and_bestindex[1])
 #The vector coerces the number to a string because the other element is a string
 #So we need to convert it
 matchcounts <- as.numeric(c(matchcounts, nearestmatch_and_bestindex[2]))
}


#Create new dataframe
top40 <- head(keyworddata, 40)
#Add to data frame
top40$nearmatch <- matchlist
#Create dataframe of the rest
matchdata <- keyworddata$Freq[41:757]
#Create an empty vector to store results
allcounts <- c()
#Loop through the indexes stored in the code above
for(i in matchcounts){
  #Print the index
  print(matchdata[i])
  #add to the vector by accessing the data at that index in matchdata
  allcounts <- c(allcounts, matchdata[i])
}
#Assign the new vector of 20 matches, as a new column
top40$matchcounts <- allcounts
#Show the whole data frame
top40
```

Let's export this along with all the other words:

```{r}
#Create new data frame with all the keywords outside the top 40
not40<-(keyworddata[c(41:length(keyworddata$Freq)),])
#Add the 2 columns that it will need to combine with the top40 matches df
not40$nearmatch <- ""
not40$matchcounts <- ""
#Combine the two
keywords.wmatches <- rbind(top40, not40)
#Export
write.csv(keywords.wmatches, "keywordswmatches.csv")
```

## Manual editing

The next stage is done in Excel: checking the top 40 against variations and adding new data...

...Once that's done, we re-import the new data - in a new notebook...